Master's Project Journal

### 2019-04-12 thesis/FPGABasedADPLLs.tex
tdll

\subsubsection{Tapped Delay Line}
To complement the asynchronous sign detection circuit, an asynchronous \ac{TDC} is also required, as otherwise there would be no benefit to using the above method over the more easily understood \ac{FSM} based design as quantisation to the clock period would happen in the \ac{TDC} rather than the sign detection circuitry. The standard method for implementing a \ac{TDC} on an \ac{ASIC} is through a tapped delay line, where a signal is propagated through a chain of fixed length delays, and at the end of the measurement interval it is recorded whether or not the signal has propagated to each point in the chain. As with the mixed signal circuitry previously addressed, a \ac{TDL} cannot be exactly replicated on an \ac{FPGA}, but through the use of inverters it is possible to replace the unrealisable fixed delays.

%TODO high level TDL image (using Z-1s)
%TODO eugene re: why no zero output

>>>>

\subsubsection{Tapped Delay Line}
To complement the asynchronous sign detection circuit, an asynchronous \ac{TDC} is also required, as otherwise there would be no benefit to using the above method over the more easily understood \ac{FSM} based design as quantisation to the clock period would happen in the \ac{TDC} rather than the sign detection circuitry. The standard method for implementing a \ac{TDC} on an \ac{ASIC} is through a tapped delay line, where a signal is propagated through a chain of fixed length delays, and at the end of the measurement interval it is recorded whether or not the signal has propagated to each point in the chain. This architecture is illustrated in Figure \ref{fig:tdl}. As with the mixed signal circuitry previously addressed, a \ac{TDL} cannot be exactly replicated on an \ac{FPGA}, but through the use of inverters it is possible to replace the unrealisable well bounded delays. As with the \ac{RO}, the delay though the inverters is not nearly as well bounded, and significant variation between delays, in both individual \ac{TDL}s and within the same \ac{TDL}, due to the implementation occurs This variation notwithstanding, the inverter pairs are a suitable replacement, and this method of time-to-digital conversion provides both resolution advantages and the presence of implementation based variation over a clocked design. These prove particularly beneficial when attempting to verify theoretical results.

Similarly to the sign at the output of the detection circuit, flip-flops store the value of each tap between phase error measurements. Prior to storage, the tap values must be converted to two's complement. As the signal propagates through the taps, magnitude of the phase error is determined by how many taps the signal has passed through. Conceptually, this thermometer coding is first converted to an unsigned integer before conversion to a signed quantity based on the sign of the error.
%TODO high level TDL image (using Z-1s)
%TODO eugene re: why no zero output
